\documentclass{article}
\usepackage{amsfonts,amssymb}
\usepackage[margin=1in]{geometry}
\usepackage{tikz}
\usetikzlibrary{arrows,automata,positioning}

\title{CSCI 480, Winter 2016\\Math Exercises \# 4}
\author{YOUR NAME HERE}
\date{Due date:  }

\begin{document}

\maketitle

\begin{itemize}
  \item
Build deterministic finite automata and/or regular expressions (as
requested) for each of the languages in questions \ref{langfirst} to
\ref{langlast}.  Create simple, meaningful automata and regular
expressions (rather than, {\em e.g.}, using the algorithm to create a
regular expression from a DFA) and explain how they work.  In all
cases the alphabet is $\Sigma = \{0,1\}$.
\item
DFAs should be specified with pictures, preferablly
typeset with {\bf TikZ}, not tables
(as tables are very hard to read).  Try to typeset them so that the
labels on the arcs are clear, {\em etc.}
\item
If you are having a difficult time with {\bf TikZ}, clear, legible
hand-drawn figures (or figures created with a drawing program)
are acceptable as graphics inclusions into your \LaTeX\ 
documents. 
\end{itemize}

\begin{enumerate}
\item
  \label{langfirst}
  The language $\{100, 10, 011\}$.

  Regular expression: 

\item   The language $\{100, 10, 011\}$.

  DFA:
    

\item The set of 
  all strings that begin or end with a doubled digit, either 11 or 00.

  Regular expression:

  
\item The set of 
  all strings that begin or end with a doubled digit, either 11 or 00.

  DFA:

  
\item
The set of all strings that have exactly one doubled digit in them.
  In other words, either 11 or 00 occurs in the string, but not both,
  and it only occurs once.

  Regular expression:
  

\item
The set of all strings that have exactly one doubled digit in them.
  In other words, either 11 or 00 occurs in the string, but not both,
  and it only occurs once.

DFA:


\item The set of all strings such that every block of three consecutive
  digits has at least two 0's in it.  Note that we have to accept
  everything with less than three digits, such as 11 and 01.

  Hint:  you may want to break the machine up into two parts, one for
  the first few letters and another for the rest, and then specify the
  complete machine as the union of the two machines.

  DFA:


\item \label{langlast} The set of all strings beginning with a 1 such
  that, interpreted as a binary representation of an integer, it has a
  remainder of 1 when divided by 3.  For example, the binary number
  $1010_b$ is decimal $10$.  When you divide 10 by 3 you get a
  remainder of 1, so $1010$ is in the language.  However, the binary
  number $1111_b$ is decimal $15$.  When you divide 15 by 3 you get a
  remainder of 0, so $1111$ is not in the language.

  Hint: if you have a binary string, such as $1100_b$, which is
  $12$ in decimal, what happens if you add a 0 to the right end?
  You get $11000_b$ which in decimal is $24$.  What happens if
  you add a 1 to the right end?  You get $11001_b$ which is decimal
  $25$. 

  DFA:
    


\item Give an example of a regular language $R$ and a nonregular
  language $N$ such that $R\cup N$ is regular.  Describe all three
  languages in English and either prove they are regular/nonregular,
  or show that they are instances of languages with known regularity.



\item Give an example of a regular language $R$ and a nonregular
  language $N$ such that $R\cup N$ is nonregular. Describe all three
  languages in English and either prove they are regular/nonregular,
  or show that they are instances of languages with known regularity.



\end{enumerate}


\end{document}
